% software development section

% Notes:
% This section is new so I'm not sure if it's only for the RnD version or not.
\section{Software Development}
\cventry{2001--2002}{Departmental Applications Development Team}{The College of New Jersey}{}{}{Served on a team of programmers responsible for implementing web-based systems.  
The systems were implemented in Perl with CGI using Oracle for data storage.  
Two of my systems were used for many years after graduation --- the online equipment distribution center and the IT budgeting system.
}

                % arguments 3 to 6 are optional
%\cventry{year--year}{Job title}{Employer}{City}{}{Description}                % arguments 3 to 6 are optional
\subsection{Proficiencies}
\cventry{10 years}{Perl}{}{}{}{
I usually prefer Perl for non-graphical implementations.
The word prediction simulations for my dissertation are written in Perl, as well as much of the dissertation support code.
I also have experience writing web applications with Perl/CGI and DBI.
}
\cventry{12 years}{Java}{}{}{}{
I prefer Java for applications with graphical interfaces, such as user evaluation of word prediction.
I also tend to use Java for XML processing, such as analysis of log files from dissertation simulations.
Also, I used Java and the JADE library to implement the vehicle-to-grid coalition server and client.
}
\cventry{10 years}{C++}{}{}{}{I use C++ mainly for academic purposes --- teaching second-semester programming/design and third-semester data structures as well as certain graduate classes (graphics).}

\cventry{familiarity}{Javascript, Python, Lua}{}{}{}{I've written small proof-of-concept applications in several other languages. Many of my systems involving web data display use Javascript to accomplish small tasks.
}
