%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}
% PhD
\cventry{2011--Present}{Ph.D. candidate in Bioengineering}{Imperial College London}{}{}{%\textit{Thesis:} Word Prediction Techniques for User Adaptation and Sparse Data Mitigation\\ 
\ifthenelse{\boolean{thesis-abstract}}{\input{sections/thesis-desc} \vspace{0.1in} \\ }{}
\textit{Supervisor:} Dr. Anil A. Bharath %\\ 
%\textit{Examiners:} Vijay Shanker, Sandra Carberry, Owen Rambow
}

% Summer School

\cventry{2012}{International Computer Vision Summer School}{University of Catania, Italy}{}{}{}{}

% MSc
\cventry{2010--2011}{MSc Biomedical Bioengineering}{Imperial College London}{	Overall mark of 71\% awarded the top mark (A) in 7/11 subjects}{}{\textit{Dissertation:} Features for the visual biopsy of polyps\\ 
\ifthenelse{\boolean{mscthesis-abstract}}{\input{sections/msc-thesis-desc} \vspace{0.1in} \\ }{}
\textit{Supervisor:} Dr. Anil A. Bharath %\\ 
%\textit{Examiners:} Vijay Shanker, Sandra Carberry, Owen Rambow
}
% MEng
\cventry{2003--2009}{MEng Telecommunications Engineering}{University of Seville}{Spain}{1st class. Specialised in Signal Processing and Radiocommunications}
{\textit{Dissertation:} IP Multimedia Subsystem (IMS), the network convergence enabler\\ 
\ifthenelse{\boolean{mengthesis-abstract}}{\input{sections/meng-thesis-desc} \vspace{0.1in} \\ }{}
\textit{Supervisor:} Dr. Alejandro Carballar %\\ 
\textit{Examiners:} Dr. Antonio Estepa, Dr. Rafael Bachiller
}
% Experts Course
\cventry{2009}{Mobile Communications Expert Course --- Technologies and Mobile Applications: GPRS/UMTS}{}{University of Seville and Vodafone Spain Foundation}{Researched on IP Multimedia Subsystem. Developed and simulated Java code for IMS service deployment on Ericsson SDS simulator}{}{}

% Highschool

\cventry{1999--2003}{Secondary studies and Spanish Bachillerato}{}{IES Albero College}{Physics, Chemistry, Maths, Biology, plus History, Spanish, English, French and Graphic design at the A2 equivalent level. Grade: 9.2/10}{}{}