%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

%------------------------------------------------

\cventry{September 2016--Present}{Machine Learning Engineer and Architect}{LaunchPad Recruits}{London, UK}{}{
  At LaunchPad Recruits I have the role of being a hybrid between a Data Engineer and a
  Data Scientist, writing code to establish flexible data pipelines that can accommodate
  from datasets of few GB to Big Data scales and make predictions with state-of-the-art
  algorithms. I also work on protoyping and productionising Machine Learning and Pattern
  Recognition algorithms for multiple data signals of all nature: text, audio and video.
  I use cutting-edge technology from systems and devops to production code of complex
  algorithms in the cloud. As a perfectionist, I love using best practices in code management
  and delivery and Agile project management.
\begin{itemize}
\item \textbf{Projects:}
\begin{itemize}
\item \textbf{Predict}, a cloud-based \underline{\href{https://www.launchpadrecruits.com/predictive-hiring}
{predictive analytics platform}} written in Python that combines machine learning and
human decision making to ensure a consistent and quicker candidate sifting whilst
reducing both the risk of missing hidden gems \& hiring unsuitable candidates.
\textit{Technologies}:
\begin{itemize}
\item \textit{Machine Learning}: Python scientific stack: scikit-learn, Numpy, Pandas, NLTK (NLP), TensorFlow, PyTorch (experimental prototypes), ...
\item \textit{Application Layer}: Flask, PostgreSQL, microservice architecture, serverless (AWS Lambda, API Gateway, CloudFormation, DynamoDB, SQS queues), S3, structlogs, AWS CloudWatch.
\item \textit{Data Science/Data Engineering tooling}: MLflow, AWS Batch, Apache Airflow, AWS Sagemaker.
\item \textit{Devops/DataOps, CI}: Docker, GitHub, Circle CI.
\end{itemize}
\item \textbf{Verify},
a \underline{\href{https://www.launchpadrecruits.com/recruitment-analytics}
{recruitment analytics platform}} written in Node.js. It is a tool that provides
insights on reviewer scoring consistency and bias aiming to ensure fairer, more
consistent hiring decisions.
\textit{Technologies}:
\begin{itemize}
\item Application Layer: Node.js (ES6), Express
\item Data Layer: PostgreSQL, Sequelize ORM, ironMQ.
\item Testing, Devops, CI: Mocha, testem, Docker, GitHub, Circle CI
\end{itemize}
\item \textbf{Project management}, I have led the implementation of a modified version of the Scrum
agile process within a Data Science team. Given its particularities, and the added difficulties of
having very specialised team members and a distributed team, it has taken some iterations to polish
but my team has achieved faster shipping timelines, less frustrations and a more lean and
iterative software delivery.
\end{itemize}
\end{itemize}
}

\cventry{2015--2016}{Data Engineer Lead}{Intern Avenue}{London, UK}{}{I was the Data
Engineer Lead at Intern Avenue, where I was in charge of multiple Big Data and machine
learning projects within the company: from recommender systems to NLP, personality
insights and data visualisation. At Intern Avenue I dedicated my efforts at developing
data analysis, feature engineering and machine learning algorithms that helped provide a better matching
between candidates looking for an internship or a graduate job and top employers.
\begin{itemize}
\item \textbf{Technologies:} recommeder system using Apache PredictionIO (Spark, Spark
MLlib, HBase), Python for data analysis, Apache Zepellin using PySpark, SparkSQL, MySQL
for Business Intelligence. Devops using Ansible, RPM packaging, Docker and deployments
in SoftLayer (IBM Cloud) bare metal servers.
\end{itemize}
}


\cventry{2014}{Summer Intern}{\textsc{The MathWorks}}{Cambridge, UK}{}{Development/Application
 Engineering team. Developed MATLAB and Simulink models that interfaced with a variety
 of sensors and actuators connected to target hardware (Arduino and Raspberry Pi)
 using I2C as communication protocol and automatic C code generation for deployment on
 target hardware:
\begin{itemize}
\item Contributed the C code to interface the I2C Linux kernel tools allowing for code
generation and deployed use on Raspberry Pi.
\item Added MATLAB and Simulink support to 6 different sensors and actuators.
\item Developed MATLAB OOP classes and examples for individual sensor/actuator operation.
\item Created Simulink sensor and actuator integration models: 10-DOF inertial
measurement unit (IMU) sensor fusion model with 3D visualization, pan and tilt unit
using microservos.
\item Developed prototypes of hardware camera stabilisation using microservos and IMU
readings, and object tracking camera using object tracking algorithms and I2C microservos.
\end{itemize}
I also expanded two current examples from the Computer Vision toolbox providing a more
robust object tracking technique and adding face tracking to the face recognition demo.
}

%\subsection{Vocational}

%\cventry{2012--Present}{1\textsuperscript{st} Year Analyst}{\textsc{Lehman Brothers}}{Los Angeles}{}{Developed spreadsheets for risk analysis on exotic derivatives on a wide array of commodities (ags, oils, precious and base metals), managed blotter and secondary trades on structured notes, liaised with Middle Office, Sales and Structuring for bookkeeping.
%\newline{}\newline{}
%Detailed achievements:
%\begin{itemize}
%\item Learned how to make amazing coffee
%\item Finally determined the reason for \textsc{PC LOAD LETTER}:
%\begin{itemize}
%\item Paper jam
%\item Software issues:
%\begin{itemize}
%\item Word not sending the correct data to printer
%\item Windows trying to print in letter format
%\end{itemize}
%\item Coffee spilled inside printer
%\end{itemize}
%\item Broke the office record for number of kitten pictures in cubicle
%\end{itemize}}

%------------------------------------------------

%\cventry{2010--2011}{Summer Intern}{\textsc{Lehman Brothers}}{Los Angeles}{}{Rated "truly distinctive" for Analytical Skills and Teamwork.}

%------------------------------------------------
%
%\subsection{Miscellaneous}
%
%\cventry{2008--2009}{Computer Repair Specialist}{Buy More}{Burbank}{}{Worked in the Nerd Herd and helped to solve computer problems by asking customers to turn their computers off and on again.}
