% publications

% notes:
% I'd like a way to turn on/off the acceptance rates

%\subsection{Journal articles}
%% this part copied from the bbl file
%\begin{thebibliography}{1}
%\bibitem{trnka08taccess}
%\bibauthor{Trnka, K.}, J.~McCaw, D.~Yarrington, and K.~F. McCoy, 2009.
%\newblock \emph{User Interaction with Word Prediction: The Effects of Prediction Quality}.
%\newblock \emph{Special Issue of ACM Transactions on Accessible Computing
%  (TACCESS) on Augmentative and Alternative Communication}, 1(3), pp. 1--34.
%\end{thebibliography}

\subsection{Journals and peer reviewed conference papers}

\begin{thebibliography}{3}

\bibitem{Rivera-Rubio2015}
\textbf{J.~Rivera-Rubio}, I.~Alexiou, and A.~A. Bharath, ``{Appearance-based indoor
  localization: A comparison of patch descriptor performance},'' {\em Pattern
  Recognition Letters}, c.~10 pages, North-Holland, 2015.

\bibitem{Rivera-Rubio2014c}
\textbf{J.~Rivera-Rubio}, I.~Alexiou, A.~Bharath, R.~Secoli, L.~Dickens, and E.~C. Lupu,
  ``{Associating locations from wearable cameras},'' in {\em British Machine
  Vision Conference (BMVC)}, c.~13 pages, Nottingham (UK), 2014.


\bibitem{Rivera-Rubio2014b}
\textbf{J.~Rivera-Rubio}, S.~Idrees, I.~Alexiou, L.~Hadjilucas, and A.~A. Bharath, ``{A
  dataset for hand-held object recognition},'' in {\em IEEE International
  Conference on Image Processing (ICIP)}, pp. 5881--5885, Paris, 2014.

\bibitem{Rivera-Rubio2014a}
\bibauthor{J.~Rivera-Rubio}, S.~Idrees, I.~Alexiou, L.~Hadjilucas, and A.~A. Bharath,
  ``{Small Hand-held Object Recognition Test (SHORT)},'' in {\em IEEE Winter
  Conference on Applications of Computer Vision (WACV)}, pp. 524--531, Steamboat Springs
  (CO, USA), 2014.

\bibitem{Rivera-Rubio2013}
\bibauthor{J.~Rivera-Rubio}, S.~Idrees, I.~Alexiou, L.~Hadjilucas, and A.~Bharath,
  ``{Mobile Visual Assistive Apps: Benchmarks of Vision Algorithm
  Performance},'' in {\em New Trends in Image Analysis and Processing -- ICIAP
  2013 SE - 4}, vol.~8158 of {\em Lecture Notes in Computer Science},
  pp.~30--40, Springer Berlin Heidelberg, 2013.

\bibitem{Rivera-Rubio2009}
\bibauthor{J.~Rivera-Rubio}, A.~Madera, and A.~Carballar, ``{Inc\'{o}gnitas de IMS y claves
  para su lanzamiento},'' in {\em Telecom I+D}, c.~4 pages, Madrid, 2009.

\bibitem{Madera2009}
A.~Madera, \bibauthor{J.~Rivera-Rubio}, and A.~Carballar, ``{DVB-H, realidad o
  ficci\'{o}n},'' in {\em Telecom I+D}, c.~4 pages, Madrid, 2009.
  
\end{thebibliography}

\subsection{Other Publications}

\begin{thebibliography}{2}

\bibitem{Rivera-Rubiotranslator2010}
\bibauthor{J.~{Rivera-Rubio (translator)}}, {\em {The peculiar memories of Thomas Penman.
  By Bruce Robinson}}.
\newblock Barcelona: Cabaret Voltaire, 1~ed., 2010.

\bibitem{Rivera-Rubio2010}
\bibauthor{J.~Rivera-Rubio}, A.~Madera, and A.~Carballar, ``{Hacia el Todo-IP en
  movilidad},'' {\em BIT}, no.~179, pp.~59--62, 2010.

\end{thebibliography}
