% research positions

\cventry{October 2011 -- Present}{PhD researcher}{Imperial College London}{PI: Dr Anil A. Bharath}{}{
During my PhD I have been involved in the following projects:
\begin{itemize}
\item Hippocampal models for localization: Proposed a biologically inspired method that uses neural networks to improve the visual recall of already visited places. 
\item Appearance-based indoor localization from wearable cameras: Developed a state-of-the-art pipeline for appearance-based localization in indoor spaces. This included the development of new descriptors based on filtering techniques that improved the performance on very ambiguous localization data, i.e. indoor corridors.
\item Sparse coding for localization: Adapted  successful techniques in image compression and denoising to create ``dictionaries of places'' for learning a representation of different routes inside a building.
\item  The RSM dataset of ``visual paths'' for benchmarking visual localization algorithms. It contains more than 1.8 km of video sequences captured with mobile and wearable devices along 6 indoor locations. I developed a benchmark to evaluate different methods using C++ and MATLAB.
\item A house-hold products dataset (the SHORT-100 dataset). SHORT-100 contains more than 150,000 images capturing usage particularities of blind and partially sighted people.
\item Picture This... project. Developed an Android app and C++ (OpenCV) backend to provide user localization based on image-matching against a previoulsy acquired dataset.
\end{itemize}
}

\cventry{October 2008 -- February 2010}{Research Assistant}{The Minerva Project: Vodafone Spain, regional Government and University of Seville R\&D project}{PI: Dr Alejandro Carballar}{}{This initiative funded my final year project. I researched on the IMS protocols and worked on R\&D project monitoring and management. I was able to work in a multidisciplinary environment, studying the applications of my main research topic in other areas of interest such as Bioengineering or Social Services.
}
%\cventry{Fall 2008 -- Fall 2009}{Research assistant}{University of Delaware}{Dr. Keith Decker}{}{Designed and implemented a multi-agent system to use a coalition of electric vehicles as a distributed battery.
%The coalition communicates with PJM (a regional transmission organization) to participate in the frequency regulation market.
%}
%\cventry{Spring 2005 -- Spring 2008}{Research assistant}{University of Delaware}{Dr. Kathleen F. McCoy}{}{Fringe word prediction project.  
%Primary researcher in adapting word prediction to the topic of discourse.  
%Primary researcher in validating the link between keystroke savings (theoretical evaluation) and communication rate (real-world evaluation).}
%\cventry{Summer 2003}{CIS Fellowship}{University of Delaware}{Dr. Sandra Carberry}{}{SIGHT project (summarizing information graphics).
%Designed annotation guidelines for information graphics and created a collection of graphics with detailed syntactic and semantic information.  
%Analyzed caption text for potential indicators of the intended communicative goal.}
